---
title: "Project-Admission Timestamp"
author: "Wanqi Geng"
date: "15 May 2020"
output: html_document
---

```{r, include=FALSE}
# General set-up for the report:
# Don't print out code
# Save results so that code blocks aren't re-run unless code
# changes (cache), _or_ a relevant earlier code block changed (autodep),
# don't clutter R output with messages or warnings (message, warning)
library(MASS)
library(knitr)
library(mapproj)
library(np)
library(ggplot2)
library(gridExtra)
library(broom)
library(dplyr)
opts_chunk$set(echo=FALSE,
               cache=TRUE, autodep=TRUE,
               message=FALSE, warning=FALSE)
# Turn off meaningless clutter in summary() output
options(show.signif.stars=FALSE)

##https://www.kaggle.com/artgor/eda-and-models#Functions-used-in-this-kernel

```

# Data analysis


## Introduction


## Exploratory data analysis
```{r, csv-read, include=FALSE}
admission_workflow_data=read.csv("C:/Users/cyh_c/Desktop/gwq/PG_Apps_Workflow_v17.csv",na.strings = c(""))
```

```{r subset1 of dataset, include=FALSE}
## will add RETURNING_DEFERRAL CURRENT_AVAIL_YEAR CURRENT_STUD_PERIOD ORGINAL_AVAIL_YEAR OGINAL_STUD_PERIOD
subset1_data = subset(admission_workflow_data,select=c(CASE_ID,STU_CITIZEN_NM,STU_ABOR_TSI_NM,STU_BIRTH_CNTRY_NM,STU_CTZN_CNTRY_NM,SUBMISSION_METHOD,ENTRY_TYPE,ASSESSMENT_DECISION_NM,ASSESSMENT_OUTCOME_NM,LAST_COUNTRY_EDUCATION,PREFERENCE_NO,AVAIL_ORG_UNIT_NM,STUDY_MODE_CD,RETURNING_DEFERRAL,CURR_AVAIL_YR,CURR_STUDY_PERIOD,ORIG_AVAIL_YR,ORIG_STUDY_PERIOD,SPK_CAT_TYPE_CD,OFFER_RELEASED_FG,OFFER_OUTCOME_CD,OFFER_CONDITIONS))
```

###Variables table
```{r discrete,echo=FALSE}
disc_names = colnames(subset1_data)[c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22)]
descriptions = c('The case ID (81265 levels)',
                 'The visa status of students (6 levels)',
                 'The Aboriginal and Torres Strait Islander status of students (6 levels)',
                 'The country of birth of students (201 levels)',
                 'The country of citizen of students (180 levels with missing values)',
                 'The application submission methods of students (6 levels with missing values)',
                 'The entry types of students(17 levels with missing values)',
                 'The assessment decision (7 levels with missing values)',
                 'The assessment outcome (7 levels with missing values)',
                 'The last country of education of students (144 levels with missing values)',
                 'The application perference number of students (7 levels)',
                 'The name of organization units of students (15 levels with wrong values "Veterinary and (&) Agricultural Sciences")',
                 'The study mode of students (5 levels: EXT=external, GOM=graduate online Melbourne, MI=mobility in, MO=mobility out, STD=standard)',
                 'The status of returning deferral (Y = YES, N = NO)',
                 'The available year after deferral(2019/2020)',
                 'The available study period after deferral(Mid Year Intake/Start Year Intake)',
                 'The available year when apply (6 levels 2016~2021)',
                 'the available study period when apply (Mid Year Intake/Start Year Intake)',
                 'The level of study of students (5 levels: CPG=?, DCW=doctor coursework, GC=graduate coursework, MCW=master coursework, PGD=phd)',
                 'The status of offer released (N = NO, Y = YES with missing values)',
                 'The outcome of offer released (5 leves with missing values $ACC = accepted, $DEC = declined, $DEF = deferred, $LAP = lapsed, $RES = resend',
                 'The status of offfer conditions (N = NO, Y = YES with missing values)')

table_disc = cbind(disc_names, descriptions)
colnames(table_disc) = c('Variable Name','Description')
kable(table_disc, digits=2, caption='Discrete Predictors')

rm(descriptions, table_disc)

```

###fix wrong/duplicate/Missing Data

```{r fix wrong values, include = FALSE}
##change the "Veterinary & Agricultural Sciences" to "Veterinary and Agricultural Sciences"
subset1_data$AVAIL_ORG_UNIT_NM=as.character(subset1_data$AVAIL_ORG_UNIT_NM)
subset1_data$AVAIL_ORG_UNIT_NM[subset1_data$AVAIL_ORG_UNIT_NM == "Veterinary & Agricultural Sciences"]<- "Veterinary and Agricultural Sciences"
subset1_data$AVAIL_ORG_UNIT_NM=as.factor(subset1_data$AVAIL_ORG_UNIT_NM)
```

```{r drop duplicate, include=FALSE}
##81265
subset1_unique_data=subset1_data[!duplicated(subset1_data),]
```

```{r replace na with Not entered,include=FALSE}
subset1_unique_data[1:22]<-lapply(subset1_unique_data[1:22],as.character)
subset1_unique_data[is.na(subset1_unique_data)] <-"Not entered"
subset1_unique_data[1:22]<-lapply(subset1_unique_data[1:22],as.factor)
```

### Response variables

```{r not-entered values-R1}
#39002
count(subset1_unique_data,OFFER_RELEASED_FG)
```

```{r not-entered values-R2}
#39002
##NA exsits 14018 not answer? maybe we can combine it with lapse109??
count(subset1_unique_data,OFFER_OUTCOME_CD)
```
```{r not-entered values-R3}
#14954
##Pre-request OFFER_RELEASED_FG == "Y"
count(subset1_unique_data,OFFER_CONDITIONS)

```

```{r values-R4}
##Pre-request:OFFER_OUTCOME_CD: $DEF
count(subset1_unique_data,RETURNING_DEFERRAL)

```
### Predict variables

```{r not-entered values-P4}
#4
count(subset1_unique_data,STU_BIRTH_CNTRY_NM)
```

```{r not-entered values-P1,include=FALSE}
#936
count(subset1_unique_data,STU_CTZN_CNTRY_NM)
```

```{r not-entered values-P2,include=FALSE}
#21
count(subset1_unique_data,SUBMISSION_METHOD)
```

```{r not-entered values-P3,include=FALSE}
#36614
count(subset1_unique_data,ENTRY_TYPE)
```

```{r not-entered values-P4,include=FALSE}
#6667
count(subset1_unique_data,ASSESSMENT_DECISION_NM)
```

```{r not-entered values-P5,include=FALSE}
#7335
count(subset1_unique_data,ASSESSMENT_OUTCOME_NM)
```

```{r not-entered values-P6,include=FALSE}
#17392
count(subset1_unique_data,LAST_COUNTRY_EDUCATION)
```

```{r predict and fill missing values1,include=FALSE}
subset1_unique_data$OFFER_RELEASED_FG=as.character(subset1_unique_data$OFFER_RELEASED_FG)
##treat "Not entered"" as "N" ? ask william 
subset1_unique_data$OFFER_RELEASED_FG <- ifelse(subset1_unique_data$OFFER_RELEASED_FG=="Not entered","N",subset1_unique_data$OFFER_RELEASED_FG)
subset1_unique_data$OFFER_RELEASED_FG=as.factor(subset1_unique_data$OFFER_RELEASED_FG)
```

```{r predict and fill missing value 1-1, include=FALSE}
##first check the visa status
##fill "Austrlia" in cells if visa status is "Australian" 
##fill "New Zealand" in cells if visa status is "New Zealander" 
subset1_unique_data$STU_CTZN_CNTRY_NM=as.character(subset1_unique_data$STU_CTZN_CNTRY_NM)
subset1_unique_data$STU_BIRTH_CNTRY_NM=as.character(subset1_unique_data$STU_BIRTH_CNTRY_NM)
subset1_unique_data$STU_CTZN_CNTRY_NM[subset1_unique_data$STU_CITIZEN_NM == "Australian"]<- "Austrlia"
subset1_unique_data$STU_CTZN_CNTRY_NM[subset1_unique_data$STU_CITIZEN_NM == "New Zealander"]<- "New Zealand"

##second check country of birth
##treat "Not entered" as values of their birth countries
subset1_unique_data$STU_CTZN_CNTRY_NM <- ifelse(subset1_unique_data$STU_CTZN_CNTRY_NM=="Not entered",subset1_unique_data$STU_BIRTH_CNTRY_NM,subset1_unique_data$STU_CTZN_CNTRY_NM)

subset1_unique_data$STU__CTZN_CNTRY_NM=as.factor(subset1_unique_data$STU_CTZN_CNTRY_NM)
subset1_unique_data$STU_BIRTH_CNTRY_NM=as.factor(subset1_unique_data$STU_BIRTH_CNTRY_NM)

#not entered remain 3
```

###Initial Summary Observations

```{r PROP TABLE}
##proportion 
prop.table(table(subset1_unique_data$STU_CITIZEN_NM))
prop.table(table(subset1_unique_data$STU_CITIZEN_NM,subset1_unique_data$OFFER_RELEASED_FG),1)

prop.table(table(subset1_unique_data$STU_ABOR_TSI_NM)
prop.table(table(subset1_unique_data$STU_ABOR_TSI_NM,subset1_unique_data$OFFER_RELEASED_FG),1)
```

We ran quick calculations to make basic observations about the dataset and found that:
35.99% of students' visa status were Australian, and ....

48.40% of students whose visa status were Australian didn't get offer, and 51.60% of students whose visa status were Australian get offer released.
```{r plot1,fig.align='center', fig.width= 8, fig.height = 10,echo=FALSE}
p1=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=STU_CITIZEN_NM),position="dodge")+ggtitle("Visa status vs. offer released")

```



```{r plot2}
p2=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=STU_ABOR_TSI_NM),position="dodge")+ggtitle("STU_ABOR_TSI_NM vs. offer released")
p2
```

```{r plot3}
p3=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=SUBMISSION_METHOD),position="dodge")+ggtitle("SUBMISSION METHOD vs. offer released")
p3
```






