---
title: "Project-Admission Timestamp--OFFER RELEASED"
author: "Wanqi Geng"
date: "25 May 2020 "
output: html_document
---

```{r, include=FALSE}
# General set-up for the report:
# Don't print out code
# Save results so that code blocks aren't re-run unless code
# changes (cache), _or_ a relevant earlier code block changed (autodep),
# don't clutter R output with messages or warnings (message, warning)
library(MASS)  
library(knitr)
library(mapproj)
library(np)
library(ggplot2)
library(gridExtra)
library(broom)
library(dplyr)
opts_chunk$set(echo=FALSE,
               cache=TRUE, autodep=TRUE,
               message=FALSE, warning=FALSE)
# Turn off meaningless clutter in summary() output
options(show.signif.stars=FALSE)

```

# Data analysis


## Introduction


## Exploratory data analysis
```{r, csv-read, include=FALSE}
admission_workflow_data=read.csv("C:/Users/cyh_c/Desktop/gwq/PG_Apps_Workflow_v17.csv",na.strings = c(""))
```

```{r subset1 of dataset, include=FALSE}
subset1_data = subset(admission_workflow_data,select=c(CASE_ID,STU_CITIZEN_NM,STU_ABOR_TSI_NM,SUBMISSION_METHOD,ENTRY_TYPE,LAST_COUNTRY_EDUCATION,PREFERENCE_NO,AVAIL_ORG_UNIT_NM,STUDY_MODE_CD,ORIG_AVAIL_YR,ORIG_STUDY_PERIOD,SPK_CAT_TYPE_CD,OFFER_RELEASED_FG))
```

###Variables table
```{r discrete,echo=FALSE}
disc_names = colnames(subset1_data)[c(1,2,3,4,5,6,7,8,9,10,11,12,13)]
descriptions = c('The case ID (81265 levels)',
                 'The visa status of students (6 levels)',
                 'The Aboriginal and Torres Strait Islander status of students (6 levels)',
                 'The application submission methods of students (6 levels with missing values)',
                 'The entry types of students(17 levels with missing values)',
                 'The last country of education of students (144 levels with missing values)',
                 'The application perference number of students (7 levels)',
                 'The name of organization units of students (15 levels with wrong values "Veterinary and (&) Agricultural Sciences")',
                 'The study mode of students (5 levels: EXT=external, GOM=graduate online Melbourne, MI=mobility in, MO=mobility out, STD=standard)',
                 #'The status of returning deferral (Y = YES, N = NO)',
                 'The available year when apply (6 levels 2016~2021)',
                 'the available study period when apply (Mid Year Intake/Start Year Intake)',
                 'The level of study of students (5 levels: CPG=?, DCW=doctor coursework, GC=graduate coursework, MCW=master coursework, PGD=phd)',
                 'The status of offer released (N = NO, Y = YES with missing values)'
                 #'The outcome of offer released (5 leves with missing values $ACC = accepted, $DEC = declined, $DEF = deferred, $LAP = lapsed, $RES = resend',
                 #'The status of offfer conditions (N = NO, Y = YES with missing values)'
                 )

table_disc = cbind(disc_names, descriptions)
colnames(table_disc) = c('Variable Name','Description')
kable(table_disc, digits=2, caption='Discrete Predictors')

rm(descriptions, table_disc)

```

###fix wrong/duplicate/Missing Data

```{r fix wrong values, include = FALSE}
##change the "Veterinary & Agricultural Sciences" to "Veterinary and Agricultural Sciences"
subset1_data$AVAIL_ORG_UNIT_NM=as.character(subset1_data$AVAIL_ORG_UNIT_NM)
subset1_data$AVAIL_ORG_UNIT_NM[subset1_data$AVAIL_ORG_UNIT_NM == "Veterinary & Agricultural Sciences"]<- "Veterinary and Agricultural Sciences"
subset1_data$AVAIL_ORG_UNIT_NM=as.factor(subset1_data$AVAIL_ORG_UNIT_NM)
```

```{r drop duplicate, include=FALSE}
##81265
subset1_unique_data=subset1_data[!duplicated(subset1_data),]
```

```{r replace na with Not entered,include=FALSE}
subset1_unique_data[1:13]<-lapply(subset1_unique_data[1:13],as.character)
subset1_unique_data[is.na(subset1_unique_data)] <-"Not entered"
subset1_unique_data[1:13]<-lapply(subset1_unique_data[1:13],as.factor)
```

### Response variables:OFFER_RELEASED_FG

```{r not-entered values-R1, include=FALSE}
#39002
count(subset1_unique_data,OFFER_RELEASED_FG)
```





```{r predict and fill missing valuesR1,include=FALSE}
subset1_unique_data$OFFER_RELEASED_FG=as.character(subset1_unique_data$OFFER_RELEASED_FG)
##treat "Not entered"" as "N"
subset1_unique_data$OFFER_RELEASED_FG <- ifelse(subset1_unique_data$OFFER_RELEASED_FG=="Not entered","N",subset1_unique_data$OFFER_RELEASED_FG)
subset1_unique_data$OFFER_RELEASED_FG=as.factor(subset1_unique_data$OFFER_RELEASED_FG)
```



###Initial Summary Observations

```{r PROP TABLE 1, echo = FALSE}
##proportion 
prop.table(table(subset1_unique_data$STU_CITIZEN_NM))
prop.table(table(subset1_unique_data$STU_CITIZEN_NM,subset1_unique_data$OFFER_RELEASED_FG),1)
```
We ran quick calculations to make basic observations about the dataset and found that:
* 36.0% of students' visa status were Australian; 
*1.0% of students' visa status were New Zealander; 
* 0.8% students' visa status were Overseas Student Residing Overseas; 
* 0.2% of students' visa status were Permanent Humanitarian Visa; 
* 4.0% of students' visa status were Permanent Resident (excl Humanitarian); 
* 58% of students' visa status were Temporary Entry Permit

* For students whose visa status were Australian,48.4% of them didn't get offer, and 51.6% of them get offer released.
* For students whose visa status were New Zealander, 46.1% of them didn't get offer, and 53.9% of them get offer released.
* For students whose visa status were Overseas Student Residing Overseas, 57.2% of them didn't get offer, and 42.8% of them get offer released.
* For students whose visa status were Permanent Humanitarian Visa, 71.6% of them didn't get offer, and 28.4% of them get offer released.
* For students whose visa status were Permanent Resident (excl Humanitarian),50.6% of them didn't get offer, and 49.4% of them get offer released.
* For students whose visa status were Temporary Entry Permit, 48.1% of them didn't get offer, and 51.9% of them get offer released.
```{r PROP TABLE 2, echo = FALSE}
prop.table(table(subset1_unique_data$STU_ABOR_TSI_NM))
prop.table(table(subset1_unique_data$STU_ABOR_TSI_NM,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 3, echo = FALSE}
prop.table(table(subset1_unique_data$SUBMISSION_METHOD))
prop.table(table(subset1_unique_data$SUBMISSION_METHOD,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 4, echo = FALSE}
prop.table(table(subset1_unique_data$ENTRY_TYPE))
prop.table(table(subset1_unique_data$ENTRY_TYPE,subset1_unique_data$OFFER_RELEASED_FG),1)
```


```{r PROP TABLE 5, echo = FALSE}
prop.table(table(subset1_unique_data$LAST_COUNTRY_EDUCATION))
prop.table(table(subset1_unique_data$LAST_COUNTRY_EDUCATION,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 6, echo = FALSE}
prop.table(table(subset1_unique_data$PREFERENCE_NO))
prop.table(table(subset1_unique_data$PREFERENCE_NO,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 7, echo = FALSE}
prop.table(table(subset1_unique_data$STUDY_MODE_CD))
prop.table(table(subset1_unique_data$AVAIL_ORG_UNIT_NM,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 8, echo = FALSE}
prop.table(table(subset1_unique_data$ORIG_AVAIL_YR))
prop.table(table(subset1_unique_data$ORIG_AVAIL_YR,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 9, echo = FALSE}
prop.table(table(subset1_unique_data$ORIG_STUDY_PERIOD))
prop.table(table(subset1_unique_data$ORIG_STUDY_PERIOD,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r PROP TABLE 10, echo = FALSE}
prop.table(table(subset1_unique_data$SPK_CAT_TYPE_CD))
prop.table(table(subset1_unique_data$SPK_CAT_TYPE_CD,subset1_unique_data$OFFER_RELEASED_FG),1)
```

```{r plot1,2,3,4,fig.align='center', fig.width= 16, fig.height = 12,echo=FALSE}
p1=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=STU_CITIZEN_NM),position="dodge")+ggtitle("visa status vs. offer released")
p2=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=STU_ABOR_TSI_NM),position="dodge")+ggtitle("aboriginal and torres strait islander status vs. offer released")
p3=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=SUBMISSION_METHOD),position="dodge")+ggtitle("submission method vs. offer released")
p4=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=ENTRY_TYPE),position="dodge")+ggtitle("entry type vs. offer released")
grid.arrange(p1,p2,p3,p4,ncol=2)
```

```{r plot5,fig.align='center', fig.width= 24, fig.height = 6,echo=FALSE}
p5=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=LAST_COUNTRY_EDUCATION),position="dodge")+ggtitle("last country of education vs. offer released")
p5
```

```{r plot6,7,8,9,10,fig.align='center', fig.width= 16, fig.height = 20,echo=FALSE}
p6=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=PREFERENCE_NO),position="dodge")+ggtitle("Prefernece number vs. offer released")
p7=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=STUDY_MODE_CD),position="dodge")+ggtitle("Study mode vs. offer released")
p8=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=ORIG_AVAIL_YR),position="dodge")+ggtitle("Original available year vs. offer released")
p9=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=ORIG_STUDY_PERIOD),position="dodge")+ggtitle("Original available period vs. offer released")
p10=ggplot(data=subset1_unique_data, aes(OFFER_RELEASED_FG,..count..))+geom_bar(aes(fill=SPK_CAT_TYPE_CD),position="dodge")+ggtitle("level of study vs. offer released")
grid.arrange(p6,p7,p8,p9,p10,ncol=2)
```







